TODO \thanks{ The original version of this paper is entitled ``Interactive Checks for Coordination Avoidance'' and was published in PVLDB Vol.\ 12. }

### 2020-05-16 doc/sigmod_paper/sections/merge_reduction.tex
Copied VLDB to SIGMOD.
I copied over the VLDB paper but ported it to the SIGMOD style files.
Now, we just have to trim!

\begin{techreport}
  The proof of \thmref{LatticeProperty} involves proving that if criteria (1)
  through (4) are met, then $O$ is \sTImergereducible{}. From this, it's
  immediate that $O$ is \sTIconfluent{} by
  \thmref{ReducibilityImpliesIconfluence}. To show that $O$ is
  \sTImergereducible, we consider two merge-free reachable expressions
  \[
    e_1 = t_1(\ldots(t_n(s_0))\ldots)
    \quad\text{and}\quad
    e_2 = u_1(\ldots(u_m(s_0))\ldots)
  \]
  Then, we inductively use criterion (3) with criteria (1) and (2) to show that
  \[
    e_3 = t_1(\ldots(
    t_n(u_1(\ldots(u_m(s_0))\ldots))
    )\ldots)
  \]
  is reachable and evaluates to $e_1 \join e_2$.
\end{techreport}

\thmref{IclosureImpliesIconfluence} states that \invariantclosure{} is a
sufficient condition for \invariantconfluence{}, and \thmref{LatticeProperty}
states that criteria (1) -- (4) are sufficient conditions for
\invariantconfluence{}. How do these sufficient conditions relate to one
another?  Clearly, not all \invariantclosed{} objects are semilattices, so
\invariantclosure{} does not imply criteria (1) -- (4). Conversely, there are
some objects which satisfy criteria (1) -- (4) which are not
\invariantclosed{}. Here's one example.

\begin{example}\examplelabel{TwoSets}
  Let $O = (\mathcal{P}(\nats), \cup)$ where $\mathcal{P}(\nats)$ is the power
  set of the natural numbers. Our start state $s_0 = \set{0}$ is the set of
  $0$. Let $t_Y(X) = X \cup Y$ be the transaction which unions $Y$ with its
  argument $X$. Our set $T = \setst{t_Y}{Y \subseteq \nats}$ of transactions
  consists of all possible $t_Y$. Our invariant $I$ consists of all non-empty
  sets $X$ that contain only even or only odd elements. That is, $I = \setst{X
  \subseteq 2\nats}{X \neq \emptyset} \cup \setst{X \subseteq 2\nats + 1}{X
  \neq \emptyset}$.

>>>>

\begin{techreport}
  To show that $O$ is \sTImergereducible, we consider two merge-free reachable
  expressions
  \[
    e_1 = t_1(\ldots(t_n(s_0))\ldots)
    \quad\text{and}\quad
    e_2 = u_1(\ldots(u_m(s_0))\ldots)
  \]
  Then, we inductively use criterion (3) with criteria (1) and (2) to show that
  \[
    e_3 = t_1(\ldots(
    t_n(u_1(\ldots(u_m(s_0))\ldots))
    )\ldots)
  \]
  is reachable and evaluates to $e_1 \join e_2$.
\end{techreport}

\thmref{IclosureImpliesIconfluence} states that \invariantclosure{} is a
sufficient condition for \invariantconfluence{}, and \thmref{LatticeProperty}
states that criteria (1) -- (4) are sufficient conditions for
\invariantconfluence{}. How do these sufficient conditions relate to one
another?  Clearly, not all \invariantclosed{} objects are semilattices, so
\invariantclosure{} does not imply criteria (1) -- (4). Conversely, there are
some objects that satisfy criteria (1) -- (4) that are not
\invariantclosed{}. Here's one example.

\begin{example}\examplelabel{TwoSets}
  Let $O = (\mathcal{P}(\nats), \cup)$ where $\mathcal{P}(\nats)$ is the power
  set of the natural numbers. Our start state $s_0 = \set{0}$ is the set of
  $0$. Let $t_Y(X) = X \cup Y$ be the transaction that unions $Y$ with its
  argument $X$. Our set $T = \setst{t_Y}{Y \subseteq \nats}$ of transactions
  consists of all possible $t_Y$. Our invariant $I$ consists of all non-empty
  sets $X$ that contain only even or only odd elements. That is, $I = \setst{X
  \subseteq 2\nats}{X \neq \emptyset} \cup \setst{X \subseteq 2\nats + 1}{X
  \neq \emptyset}$.
